A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-03-02 2022/Sensors/sensors.tex
first virsion of figures
Title and Abstract

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}
		   %Acceleration of Global Optimization Algorithm by Detecting Local Extrema Based on Machine Learning

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
abstract
}

@@

\begin{figure}
\includegraphics[width=0.6\linewidth]{Definitions/logo-mdpi}
\caption{Using GSA-DT algorithm to solve GKLS problems}
\label{fig4}
\end{figure}

@@

\end{paracol}
\begin{figure}	
\widefigure
\includegraphics[width=15 cm]{Definitions/logo-mdpi}
\caption{This is a wide figure.\label{fig2}}
\end{figure}  
\begin{paracol}{2}
\linenumbers
\switchcolumn

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Fast kNN Algorithm Using Multiple Space-Filling Curves}
		   %Acceleration of Global Optimization Algorithm by Detecting Local Extrema Based on Machine Learning

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{
The paper considers a time-efficient implementation of the k-nearest neighborhood (kNN) algorithm. A well-known approach for accelerating the kNN algorithm is to utilize dimensionality reduction methods based on the use of space-filling curves. In this paper, we take this approach further and propose an algorithm that employs multiple space-filling curves and is faster (with comparable quality) compared to the kNN algorithm which uses kd-trees to determine the nearest neighbors. A specific method for constructing multiple Peano curves is outlined, and statements are given about the preservation of object proximity information in the course of dimensionality reduction. An experimental comparison with known kNN implementations using kd-trees was performed using test and real-life data.
}

@@

\begin{figure}
\center
\includegraphics[width=0.5\linewidth]{fig1.png}
\caption{Using GSA-DT algorithm to solve GKLS problems}
\label{fig1}
\end{figure}

@@

\end{paracol}

\begin{figure}	
\widefigure
\includegraphics[width=1.0\linewidth]{fig2.png}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{paracol}{2}
\linenumbers
\switchcolumn
